Extracting The Power of Dependent Types

### 2021-07-14 paper.tex
Move an example to the introduction

In order to keep presentation as simple as possible, we have
chosen a very simple target language to embed --- we use a subset
of PostScript~\cite{}, which is a stack-based
language used in the corresponding document format.  While the embedding
may look impractical, the simplicity of the language
allows us to focus on the essence of the proposed approach and avoid unrelated
technical details.  We ensure that many verification patterns found in bigger
languages are covered, showing that the proposed approach scales.

>>>>

\input{latex/intro-example}

To keep presentation as simple as possible, we have
chosen a very simple target language to embed --- we use a subset
of PostScript~\citep{postscript1999language}, a stack-based
language used in the corresponding document format.
%
\figref{sqsum} shows an example of a program
written in our embedding and the PostScript code produced by
our extractor.
%
While the embedding may look simplistic, this simplicity
allows us to focus on the essence of the proposed approach and avoid unrelated
technical details.  We ensure that many verification patterns found in bigger
languages are covered, showing that the proposed approach scales.
